Efficient Constructions of Prefer-Max Sequences and of Infinite de Bruijn Sequences

### 2017-01-10 paper.tex
m --> n in the proof of the Onion theorem

		For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that
		$w_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$ letters suffix of
		$w$. Because zero is the smallest symbol in our alphabet, we get that it is
		added by the prefer-max rule only if all the other symbols cannot be added,
		i.e., when adding other symbols would generate a substring that has already
		being seen before. Since $w$ comes, as a window, right before a word of the
		form $w[2..m]\tau$ for some $\tau \geq 0$, we have that $w[2..m]0$ comes after
		(or is equal to) $w[2..m]\tau$ which is after $w$. Similar arguments give us
		that $w[2..m]0$ appears before $w[3..m]0^2$ which appears before $w[4..m]0^3$
		and so on. Together we get that $j_1 < j_2 < \cdots < j_n$. Note that
		$w_{j_1}=w$, i.e, that $w$ appears as a substring at the $j_1$'s symbol of the
		sequence.

>>>>

		For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that
		$w_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$ letters suffix of
		$w$. Because zero is the smallest symbol in our alphabet, we get that it is
		added by the prefer-max rule only if all the other symbols cannot be added,
		i.e., when adding other symbols would generate a substring that has already
		being seen before. Since $w$ comes, as a window, right before a word of the
		form $w[2..n]\tau$ for some $\tau \geq 0$, we have that $w[2..n]0$ comes after
		(or is equal to) $w[2..n]\tau$ which is after $w$. Similar arguments give us
		that $w[2..n]0$ appears before $w[3..n]0^2$ which appears before $w[4..n]0^3$
		and so on. Together we get that $j_1 < j_2 < \cdots < j_n$. Note that
		$w_{j_1}=w$, i.e, that $w$ appears as a substring at the $j_1$'s symbol of the
		sequence.
